Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-09 talk/index.Rmd
talk: added bullet to discussion

`r icon_style(icons::fontawesome("bullseye"), scale = 1.5, fill = "#035AA6")`   $~~~$ Crowdsourced data analysis has **many worthy uses**  
--

@@

>>>>

`r icon_style(icons::fontawesome("route"), scale = 1.5, fill = "#035AA6")`   $~~~$ Crowdsourced data analysis has **many worthy uses**  
--

@@

`r icon_style(icons::fontawesome("comments"), scale = 1.5, fill = "#035AA6")` $~$ Importance of **science communication** and **communicating uncertainty**  
--
